SDR enhancement by clouds \\\large{A Short Subtitle}

### 2024-02-22 article/article.qmd
Commit 2024-02-22 12:14

```{r setup, echo=F, include=T, warning=FALSE, message=FALSE}
suppressMessages(
    res <- rmarkdown::find_pandoc(dir = '/usr/lib/rstudio/resources/app/bin/quarto/bin/tools')
)
## document configurations
knitr::opts_chunk$set(comment    = ""      )
# knitr::opts_chunk$set(dev        = "pdf"   )
knitr::opts_chunk$set(out.width  = "70%"   )
knitr::opts_chunk$set(fig.align  = "center")
knitr::opts_chunk$set(fig.pos    = 'h!'    )
options(knitr.graphics.auto_pdf = FALSE)
library(pander)
library(data.table)
library(kableExtra)
library(dplyr)
## load data from trends analysis
source("~/MANUSCRIPTS/02_enhancement/GHI_enh_00_variables.R")
TSIinfo <- data.table(read.csv("~/MANUSCRIPTS/02_enhancement/figures/tbl_tsi_info.dat",
                    strip.white = TRUE,
                    sep = ";",
                    header = TRUE))
# ## create local citations file and links here
# source("~/CODE/FUNCTIONS/R/gather_citations.R")
# suppressMessages(
#     gather_citations(
#         sourcefile   = "./Article.Rmd",
#         mainreposit  = "./Mainreferences.bib",
#         localreposit = "./references.bib",
#         folderlink   = "./References_links",
#         workingdir   = "./"
#     )
# )
```

@@

$$
f(x)=\begin{cases}
1, & \text{if $x<0$}.\\
0, & \text{otherwise}.
\end{cases}
$$

>>>>

```{r setup, echo=F, include=T, warning=FALSE, message=FALSE}
suppressMessages(
    res <- rmarkdown::find_pandoc(dir = '/usr/lib/rstudio/resources/app/bin/quarto/bin/tools')
)
## document configurations
knitr::opts_chunk$set(comment    = ""      )
# knitr::opts_chunk$set(dev        = "pdf"   )
knitr::opts_chunk$set(out.width  = "70%"   )
knitr::opts_chunk$set(fig.align  = "center")
knitr::opts_chunk$set(fig.pos    = 'h!'    )
options(knitr.graphics.auto_pdf = FALSE)
library(pander)
library(data.table)
library(kableExtra)
library(dplyr)
## load data from trends analysis
source("~/MANUSCRIPTS/02_enhancement/GHI_enh_00_variables.R")
load("~/MANUSCRIPTS/02_enhancement/data/GHI_enh_03_process.Rda")
TSIinfo <- data.table(read.csv("~/MANUSCRIPTS/02_enhancement/figures/tbl_tsi_info.dat",
                    strip.white = TRUE,
                    sep = ";",
                    header = TRUE))
# ## create local citations file and links here
# source("~/CODE/FUNCTIONS/R/gather_citations.R")
# suppressMessages(
#     gather_citations(
#         sourcefile   = "./Article.Rmd",
#         mainreposit  = "./Mainreferences.bib",
#         localreposit = "./references.bib",
#         folderlink   = "./References_links",
#         workingdir   = "./"
#     )
# )
```

@@

$$
\text{CE}_\text{Threshold} = \begin{cases}
`r C4_cs_ref_ratio`, & \text{if $\theta \leq `r C4_lowcut_sza`^\circ$}.\\
\frac{`r C4_cs_ref_ratio` - `r C4_lowcut_ratio`}{`r C4_lowcut_sza` - `r 90 - BIO_ELEVA`} \cdot (\theta- `r 90 - BIO_ELEVA`) + `r C4_lowcut_ratio` , & \text{if $ `r 90 - BIO_ELEVA`^\circ > \theta > `r C4_lowcut_sza`^\circ$}.
\end{cases}
$${#eq-test}

### 2024-02-22 article/article.tex
Commit 2024-02-22 12:14

\begin{keyword}
    keyword1 \sep 
    keyword2
\end{keyword}
\end{frontmatter}
    \ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[enhanced, borderline west={3pt}{0pt}{shadecolor}, frame hidden, interior hidden, breakable, sharp corners, boxrule=0pt]}{\end{tcolorbox}}\fi

@@

\[
f(x)=\begin{cases}
1, & \text{if $x<0$}.\\
0, & \text{otherwise}.
\end{cases}
\]

@@

\begin{tcolorbox}[enhanced jigsaw, bottomrule=.15mm, title=\textcolor{quarto-callout-important-color}{\faExclamation}\hspace{0.5em}{gcff}, bottomtitle=1mm, colback=white, rightrule=.15mm, breakable, toptitle=1mm, toprule=.15mm, colframe=quarto-callout-important-color-frame, opacityback=0, leftrule=.75mm, opacitybacktitle=0.6, coltitle=black, left=2mm, titlerule=0mm, arc=.35mm, colbacktitle=quarto-callout-important-color!10!white]

>>>>

\begin{keyword}
    keyword1 \sep 
    keyword2
\end{keyword}
\end{frontmatter}
    \ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[sharp corners, frame hidden, boxrule=0pt, breakable, borderline west={3pt}{0pt}{shadecolor}, interior hidden, enhanced]}{\end{tcolorbox}}\fi

@@

\begin{equation}\protect\hypertarget{eq-test}{}{
\text{CE: GHI} > \begin{cases}
1.05, & \text{if $\theta \leq 60^\circ$}.\\
1.18, & \text{if $ 80^\circ > \theta > 60^\circ$}.
\end{cases}
}\label{eq-test}\end{equation}

@@

\begin{tcolorbox}[enhanced jigsaw, opacityback=0, leftrule=.75mm, coltitle=black, breakable, bottomrule=.15mm, colbacktitle=quarto-callout-important-color!10!white, colframe=quarto-callout-important-color-frame, left=2mm, titlerule=0mm, bottomtitle=1mm, colback=white, arc=.35mm, toptitle=1mm, title=\textcolor{quarto-callout-important-color}{\faExclamation}\hspace{0.5em}{gcff}, rightrule=.15mm, toprule=.15mm, opacitybacktitle=0.6]
